Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-12-18 ms.tex
I added an equation for the re-parameterized two temperature model.
I put in a plot with the MCMC posteriors for a 2 temperature model.

@@

>>>>

In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
There-fore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
\begin{equation}\label{eq:2tempAdiff}
A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
\end{equation}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_fit_2temp.pdf}
\caption{Example posterior distributions for an MCMC fit to the spectra using Equation \ref{eq:2tempAdiff}.}\label{fig:post2Tempfit}
\end{centering}
\end{figure}
